Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-09-25 manuscript/paper-tycho.tex
New Kepler, CasA regions; run Tycho pipeline
New Kepler regions should be clean of thermal emission
Cas A regions to give sense of counts / energy bands / profile shapes
Docs to run pipelines, etc.  Minor paper updates

We selected 13 regions in 5 distinct filaments around Tycho's shock
(Figure~\ref{fig:snr}) based on the following criteria: (1) filaments should be
clear of spatial plumes of thermal ejecta in \Chandra images, which rules out,
e.g., areas of strong thermal emission on Tycho's eastern limb; (2) filaments
should be singular and localized; multiple filaments should either not
overlap or completely overlap (rules out parts of NE limb); (3) filaments
should have clear FWHMs in most energy band; i.e., a peak should be evident
above the background signal or downstream thermal emission (rules out some
faint southern wisps) \note[Aaron]{wishy-washy qualitative}.  We grouped
regions into filaments by visual inspection of the remnant.

>>>>

% KEEP REGION NUMBER UPDATED
We selected 22 regions in 5 distinct filaments around Tycho's shock
(Figure~\ref{fig:snr}) based on the following criteria: (1) filaments should be
clear of spatial plumes of thermal ejecta in \Chandra images, which rules out,
e.g., areas of strong thermal emission on Tycho's eastern limb; (2) filaments
should be singular and localized; multiple filaments should either not
overlap or completely overlap (rules out parts of NE limb); (3) filaments
should have clear FWHMs in most energy band; i.e., a peak should be evident
above the background signal or downstream thermal emission (rules out some
faint southern wisps) \note[Aaron]{wishy-washy qualitative}.  We grouped
regions into filaments by visual inspection of the remnant.
Within each filament, we chose region widths to get a similar number of counts
at the thin rim, in each region. \note[Aaron]{wording}
We attempted to balance signal-to-noise of each profile against having multiple
selections for each filament (a signal-to-noise further downstream, in a
sense); within each filament we tried to keep the number of counts in each
region
